---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(GSPQualtricsR)
data("feb_omnibus")
```

# GSPQualtricsR

<!-- badges: start -->
<!-- badges: end -->

GSPQualtricsR provides an interface to download and work through Qualtrics surveys. It was written for primary usage through this Shiny app, however it can be used in R directly. Code to process the survey in R (wihthout using the app) is below. 

## Installation

You can install the development version of GSPQualtricsR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("taylorgrant/GSPQualtricsR")
```

## Functionality

This package assumes that you have grabbed your API key and base URL from Qualtrics and saved these to the .Renviron as `QUALTRICS_KEY` and `QUALTRICS_BASE_URL`. See [here](https://api.qualtrics.com/) for information about Qualtrics API. 

### Fetch SIDs 

Qualtrics surveys are defined by an ID. These can be retrieved by using the following function `fetch_sids()`, which returns the ID, survey name, the owner of the survey, date the survey was last modified, the date it was created, and whether the survey is active.  

```{r, eval = FALSE}
sids <- fetch_sids()
head(sids)
```

```{r, echo = FALSE}
head(feb_omnibus$sids)
```

### Fetch the survey of interest

With this data, we can then use the function `fetch_survey_data()` to fetch the survey of interest. This function relies on some of the [qualtRics](https://cran.r-project.org/web/packages/qualtRics/vignettes/qualtRics.html) package for some ingest code, but it's been modified to download the survey in an SPSS rather than csv format (this is useful because the data comes in a [haven](https://haven.tidyverse.org/) format that is both labelled and numeric). The function also creates a Table of Contents for all questions in the survey as well any user generated variables that were created within Qualtrics and published with the data (any user generated variables should start with a lower case "x" to be found and recognized by the function).  

From the sids, we'll download the February Omnibus  

```{r, eval = FALSE}
data <- fetch_survey_data(sid = sids$id[2])
```

The function returns a list that includes (1) the survey data (in an `as_survey_design()` format via the [srvyr](https://cran.r-project.org/web/packages/srvyr/vignettes/srvyr-vs-survey.html) package) and (2) the Table of Contents that includes information for each question. 

#### Table of Contents

The Table of Contents contains the Survey Block, the question order, the export name (a user friendly question number), the question type (multiple choice, text field, etc.), the text of the question, whether there is a sub-label associated with the question (normally found in a grid or matrix question), and the selector type (we really only care about Likerts in this case).  

```{r, eval = FALSE}
head(data$toc)
```

```{r, echo = FALSE}
head(feb_omnibus$toc)
```

#### Survey

The survey data is in a survey design and all analysis under the hood is conducted using the `srvyr` package. To see the raw survey data, you can use the following (truncated): 

```{r, eval = FALSE}
head(data$svy$variables, 4)
```

```{r, echo = FALSE}
head(feb_omnibus$svy$variables[,1:10], 4)
```

### Analysis 

This package makes analysis very simple via the wrapper function `summarize_question()`. All that we have to do is define some parameters. 

The parameters that we can use are:

 - **qid** - the `question_id` found in the Table of Contents
 - **gid** - the `question_id` of any variable that we want to use as the crosstab selection
 - **fiq** - the filters we want to apply; e.g., do we only want to include women in the analysis of the question. `fiq` is a list that includes the filter question (called by the `export_name` from the TOC) and the filter choices that should be included
 - **ci** - the confidence interval to use for hypothesis testing
 - **top_box / bottom_box** - if the qid is a Likert scaled question, do we want to summarize by Top N Box / Bottom N Box
 
The returned results include significance tests based on the confidence interval set by the user. 

If this seems a little complicated, it probably is because this package was intended to be used with a Shiny app. 

**The rest of this won't contain results, just code:** 

#### Single Question Analysis (no crosstab)

We'll start with a simple analysis without a crosstab. Any call to `summarize_question()` is going to return a list with two dataframes - `out_win` and `out_bwn`. If there is no crosstab, then `out_bwn` is NULL. 

We're going to look to a specific variable - Q15 - that asks respondents what it was that they enjoyed about this year's Super Bowl ads. 

```{r, eval = FALSE}
data$toc |> dplyr::filter(stringr::str_detect(export_name, "^Q15"))
```

```{r, echo = FALSE}
feb_omnibus$toc |> dplyr::filter(stringr::str_detect(export_name, "^Q15"))
```

```{r, eval = FALSE}
parameters = list(qid = "QID2701", gid = NULL, fiq = NULL, ci = .9)
tbl <- summarize_question(parameters, data = data)
```

The object `tbl` is a list and it will have some data that we don't really need. But we can use a helper function to create a DT table that takes all necessary data. 

```{r, eval = FALSE}
build_table(tbl$out_win, ci = .9)
```

#### Crosstabbed Question Analysis

Say we wanted to crosstab the question by respondent's generation. 

```{r, eval = FALSE}
parameters = list(qid = "QID2722", gid = "QID2422b", fiq = NULL, ci = .9)
tbl <- summarize_question(parameters, data = data)
```

Again `tbl` is a list, and we're most interested in the `tbl$out_bwn` which is capturing any statistical signifiance between the crosstabbed groups, in this case our generations. 

```{r, eval = FALSE}
build_table(tbl$out_bwn, ci = .9)
```

#### Filter Usage

Assume we wanted to filter our responses to only include Females. To find the variable for Females, we would look to the Table of Contents, find our Gender variable and then access the raw data to look to the coding. Filter work for single variable and crosstabbed summaries. 

```{r, eval = FALSE}
parameters = list(qid = "QID2701", gid = NULL, fiq = list(filterQ = "Q2", filter_choices = c("1")), ci = .9)
tbl <- summarize_question(parameters, data = data)
```

#### Top Box / Bottom Box

We're switching our `qid` variable to a Likert scaled question. And then, just as we did to identify the filter variable, we find the numeric values that are the top and bottom box. We then simply add them to the parameters. 
```{r, eval = FALSE}
parameters = list(qid = "QID2722", gid = "QID2422b", fiq = NULL, ci = .9, top_box = c("5", "6"), bottom_box = c(2,3))
tbl <- summarize_question(parameters, data = data)
```

#### Summarizing a Whole Block

Finally, we can summarize an entire survey block using the following. Entire survey blocks can be crosstabbed and filtered, but because there are sometimes multiple Likert scales within a single block, it wasn't feasible to include the ability to Top/Bottom box. 

When we summarize a block, the data is returned in a large list, each question in the block includes the same `out_win` and `out_bwn` tables. But because the list is one level deeper than we want there is a bit of extra code required from the user. Next, we want to export the data in a nicely formatted excel doc. 

```{r, eval = FALSE}
parameters = list(qid = "QID2722", gid = "QID2422b", fiq = NULL, ci = .9)
tbl <- summarize_block("SuperBowl", parameters, data)
tbl <- unlist(tbl,recursive=FALSE)
openxlsx::write.xlsx(tbl, "~/Desktop/superbowl_block.xlsx")
```

